NumPy---Array Programming in Python

### 2020-02-05 authors.tex
Update Eric's institution
Update Marten's initial
Minor updates

\author[1]{Charles R Harris}
\author[2,3,*]{K. Jarrod Millman}
\author[2,*]{St\'efan J. van der Walt}
\author[4,*]{Ralf Gommers}
\author[5]{Pauli Virtanen}
\author[6]{David Cournapeau}
\author[7]{Eric Wieser}
\author[80]{Julian Taylor}
\author[2]{Sebastian Berg}
\author[9]{Nathaniel J. Smith}
\author[10]{Robert Kern}
\author[2]{Matti Picus}
\author[11]{Stephan Hoyer}
\author[12]{Marten van Kerkwijk}
\author[13]{Matthew Brett}
\author[14]{Allan Haldane}
\author[15]{Jaime Fernandez del Rio}
\author[16]{Mark Wiebe}
\author[4,17,18]{Pearu Peterson}
\author[80]{David M. Cooke}
\author[20]{Pierre Gerard-Marchant}
\author[21]{Kevin Sheppard}
\author[22]{Tyler J. Reddy}
\author[2]{Warren Weckesser}
\author[4]{Hameer Abbasi}
\author[23]{Christoph Gohlke}
\author[4]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, CA, USA}
\affil[4]{Quansight LLC, Austin, TX, USA}
\affil[5]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[6]{Mercai JP, Tokyo, Japan}
\affil[7]{University of Cambridge, Cambridge, UK}
\affil[9]{Independent Researcher, Berkeley, CA, USA}
\affil[10]{Enthought, Inc., Austin, TX, USA}
\affil[11]{Google Research, Mountain View, CA, USA}
\affil[12]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[13]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[14]{Department of Chemistry, Temple University, Philadelphia, PA, USA}
\affil[15]{Google, Zurich, Switzerland}
\affil[16]{AWS Thinkbox, Seattle, Washington, USA}
\affil[17]{Independent Researcher, Saue, Estonia}
\affil[18]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[20]{France-IX, France}
\affil[21]{Department of Economics, University of Oxford, Oxford, UK}
\affil[22]{Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[24]{Biomedical Engineering Department, University of California, Irvine, USA}
\affil[80]{Not sure}
\affil[*]{numpy.articles@gmail.com}

>>>>

\author[1]{Charles R Harris}
\author[2,3,*]{K. Jarrod Millman}
\author[2,*]{St\'efan J. van der Walt}
\author[4,*]{Ralf Gommers}
\author[5]{Pauli Virtanen}
\author[6]{David Cournapeau}
\author[7]{Eric Wieser}
\author[80]{Julian Taylor}
\author[2]{Sebastian Berg}
\author[9]{Nathaniel J. Smith}
\author[10]{Robert Kern}
\author[2]{Matti Picus}
\author[11]{Stephan Hoyer}
\author[12]{Marten H. van Kerkwijk}
\author[13]{Matthew Brett}
\author[14]{Allan Haldane}
\author[15]{Jaime Fernandez del Rio}
\author[16]{Mark Wiebe}
\author[4,17,18]{Pearu Peterson}
\author[80]{David M. Cooke}
\author[20]{Pierre Gerard-Marchant}
\author[21]{Kevin Sheppard}
\author[22]{Tyler J. Reddy}
\author[2]{Warren Weckesser}
\author[4]{Hameer Abbasi}
\author[23]{Christoph Gohlke}
\author[4]{Travis E. Oliphant}
\affil[1]{Independent Researcher, Logan, Utah, USA}
\affil[2]{Berkeley Institute for Data Science, University of California, Berkeley, Berkeley, CA, USA}
\affil[3]{Division of Biostatistics, University of California, Berkeley, Berkeley, CA, USA}
\affil[4]{Quansight LLC, Austin, TX, USA}
\affil[5]{Department of Physics and Nanoscience Center, University of Jyv\"askyl\"a, Jyv\"askyl\"a, Finland}
\affil[6]{Mercai JP, Tokyo, Japan}
\affil[7]{Department of Engineering, University of Cambridge, Cambridge, UK}
\affil[9]{Independent Researcher, Berkeley, Berkeley, CA, USA}
\affil[10]{Enthought, Inc., Austin, TX, USA}
\affil[11]{Google Research, Mountain View, CA, USA}
\affil[12]{Department of Astronomy \& Astrophysics, University of Toronto, Toronto, ON, Canada}
\affil[13]{School of Psychology, University of Birmingham, Edgbaston, Birmigham, UK}
\affil[14]{Department of Chemistry, Temple University, Philadelphia, PA, USA}
\affil[15]{Google, Zurich, Switzerland}
\affil[16]{AWS Thinkbox, Seattle, Washington, USA}
\affil[17]{Independent Researcher, Saue, Estonia}
\affil[18]{Department of Mechanics and Applied Mathematics, Institute of Cybernetics at Tallinn Technical University, Tallinn, Estonia}
\affil[20]{France-IX, France}
\affil[21]{Department of Economics, University of Oxford, Oxford, UK}
\affil[22]{Los Alamos National Laboratory, Los Alamos, NM, USA}
\affil[24]{Biomedical Engineering Department, University of California, Irvine, Irvine, CA, USA}
\affil[80]{Not sure}
\affil[*]{numpy.articles@gmail.com}
